Data simulations

### 2019-08-28 analysis/data_simulations.Rmd
add some more simulations

n_sub = 100

@@

tibble(id = 1:n_sub) %>% 
  mutate(tidy = map(id, rmvBinomial, n =n_trials, size=size, p1=p1, p2=p2, rho=rho))%>%
  unnest(tidy)%>%
  group_by(id, task)%>%
  summarise(mean= mean(score))%>%
  spread(task, mean)%>%
  ungroup()%>%
  summarise(cor = cor(V1,V2))

@@

@@

ggplot(sim_plot_cor, aes(x = cor, fill = trials))+
  geom_density(alpha = .5)+
  geom_vline(xintercept = .3)+
  xlim(0,1)+
  theme_few()+
  scale_fill_ptol()
```

>>>>

n_sub = 50

@@

tibble(id = 1:n_sub) %>% 
  mutate(tidy = map(id, rmvBinomial, n =n_trials, size=size, p1=p1, p2=p2, rho=rho))%>%
  unnest(tidy)%>%
  group_by(id, task)%>%
  summarise(mean= mean(score))%>%
  spread(task, mean)%>%
  ungroup()%>%
  summarise(correl = cor(V1,V2))

@@

n_sim = 100

@@

ggplot(sim_plot_cor, aes(x = correl, fill = trials))+
  geom_density(alpha = .5)+
  geom_vline(xintercept = .3)+
  xlim(0,1)+
  theme_few()+
  scale_fill_ptol()
```

```{r}
ggsave("../graphs/n100_rho03.pdf", width = 5, height = 4, scale = 1.5)
```
